### 2018-01-31 CO749-GraphColoring/assignments/A2.tex
Finished 4

>>>>

	We proceed by induction on $i$. If $i = 2$ then we observe that all colors of $L(v_3) - c$ are left for the same reason as for $v_2$, i.e. since there are no odd vertices left of $v_3$ that are not $v_1$.
	So for induction we suppose $i>2$ and the claim holds for vertices $v_j$ with $2\leq j < i$. Then by a simple induction we can show since $v_2$ is left, all of $v_2\dots v_i$ are left. If $v_i$ is even then each left color of $v_i$ is a left color of $v_{i+1}$ since its corresponding path component cannot have its rigthmost vertex be $v_i$. Further any left color $c'$ of $v_{i+1}$ is a left color of $v_i$. To see this, observe by Claim $4.2$ a color is either left or right, and since $v_{i+1}$ is odd, if then $c'$-corresponding path component had leftmost vertex $v_{i+1}$ then $c'$ would be left. Hence $v_{i+1}$ has an odd number of left colors and so $v_{i+1}$ is left, as desired.
	So we may assume that $v_i$ is odd. Then $v_{i+1}$ is even. So by a similar argument to the above, $v_i$ and $v_{i+1}$ have the same right colors. By Claim $4.3$, $v_i$ is not right so $v_{i+1}$ has an even number of right colors and hence is not right. Thus by Claim $4.3$, $v_{i+1}$ is left, as desired. By induction the Claim is proven.
